---
title: "Logistic classifier"
output: html_notebook
---

# load packages

```{r}
library(stats)
library(dplyr)
library(boot)
library(ISLR2)
library(MASS)
library(ROCR)
library(ggplot2)
getwd()
```


# load data here
```{r}
data2=read.csv('all_aucs.csv')
#data2=read.csv('clustCCFdecshift_seek.csv')
data2$Cluster=factor(data2$block)
data2=data2 %>% na.omit()
data2norm=as.data.frame(data2) 
#data2$Block=factor(data2$sk_Block)


#data2norm=scale(data2[3:7]) %>% as.data.frame() # 7 for mpfcsk
#data2norm=as.data.frame(data2) 
#data2norm$Cluster=factor(data2$Cluster)
#data2norm$Block=factor(data2$Block)
train3=data2norm %>% filter(Cluster=='3') %>% sample_n(50)
train1=data2norm %>% filter(Cluster=='1') %>% sample_n(50)
train=rbind(train1,train3)

trainshuf=transform( train, Cluster = sample(Cluster))
```
data2norm$Change=scale(data2norm$Pre)
data2norm$Sum=scale(data2norm$Post)
data2norm$Food=scale(data2norm$Food)
data2norm$ofcChange=scale(data2norm$ofcChange)
data2norm$ofcSum=scale(data2norm$ofcSum)
data2norm$ofcFood=scale(data2norm$ofcFood)


data2norm=data2norm[sample(1:nrow(data2norm)), ]


#data vis
```{r}
ggplot(data2norm,aes(x=Food,y=Sum,color=Cluster))+geom_point(size=3,alpha=.4)+theme_classic()
```

```{r}
glm.fits<-glm(Cluster~Change+Sum+Food,data=train,family=binomial)
summary(glm.fits)
```

```{r}
glm.fits<-glm(Cluster~sk+tk+Food,data=train,family=binomial)
glm.probs<- predict(glm.fits,type='response')
glm.pred<- rep("1",200) # make other state
glm.pred[glm.probs > .5] = '3' #make a given state
table(glm.pred,train$Cluster)
mean(glm.pred == train$Cluster)
```

```{r}
glm.pred<- rep("1",443) # make other state
glm.pred[glm.probs > .5] = '3' #make a given state
table(glm.pred,data2$Cluster)
mean(glm.pred == data2$Cluster)#probability of correct prediction for training set
```


# add LOOCV here
```{r}
cv.err<-cv.glm(data2,glm.fits,K=10)
cv.err$delta
```




#LDA
```{r}
lda.fitCV<-lda(Cluster~Pre*Post*tPre*tPost*Food,CV=TRUE,method='mle',data=train)
a=table(train$Cluster, lda.fitCV$class, dnn = c('Actual Group','Predicted Group'))
(a[4]+a[1])/200
```

```{r}
lda.fitCV<-lda(Cluster~Change+Food+Change.take.,CV=TRUE,method='mle',data=datashuf)
table(datashuf$Cluster, lda.fitCV$class, dnn = c('Actual Group','Predicted Group'))
```

```{r}

vals=c()
OFCvals=c()
samples=20
sessiontoget='STPre'
region='mPFC'
region2='mPFC'

for (i in 1:40){
  train3=data2norm %>% filter(Cluster=='3') %>% filter(Region == region)%>% filter(sk_Session == sessiontoget)%>% sample_n(samples)
  train2=data2norm %>% filter(Cluster=='2') %>% filter(Region == region)%>% filter(sk_Session == sessiontoget)%>% sample_n(samples)
  train1=data2norm %>% filter(Cluster=='1') %>% filter(Region == region)%>% filter(sk_Session == sessiontoget)%>% sample_n(samples)
  train=rbind(train1,train2,train3)
  
  OFCtrain3=data2norm %>% filter(Cluster=='3') %>% filter(Region == region2)%>% filter(sk_Session == sessiontoget)%>% sample_n(samples)
  OFCtrain2=data2norm %>% filter(Cluster=='2') %>% filter(Region == region2)%>% filter(sk_Session == sessiontoget)%>% sample_n(samples)
  OFCtrain1=data2norm %>% filter(Cluster=='1') %>% filter(Region == region2)%>% filter(sk_Session == sessiontoget)%>% sample_n(samples)
  OFCtrain=rbind(OFCtrain1,OFCtrain2,OFCtrain3)
  #train=transform(train, Cluster = sample(Cluster))
  #trainshuf=transform( train, Cluster = sample(Cluster))
  #lda.fitCV<-lda(Cluster~Pre*Post+tPre*tPost,CV=TRUE,data=train)
  lda.fitCV<-lda(Cluster~nolag,CV=TRUE,data=train)
  OFClda.fitCV<-lda(Cluster~nolag,CV=TRUE,data=OFCtrain)
  
  #OFClda.fitCV<-lda(Cluster~sk_Change+tk_Sum+tk_Food,CV=TRUE,data=OFCtrain)
  

  
  
  
  a=table(train$Cluster, lda.fitCV$class, dnn = c('Actual Group','Predicted Group'))
  acc=(a[1]+a[5]+a[9])/(samples*3)
  vals=c(vals,acc)
  
  
  OFCa=table(OFCtrain$Cluster, OFClda.fitCV$class, dnn = c('Actual Group','Predicted Group'))
  OFCacc=(OFCa[1]+OFCa[5]+OFCa[9])/(samples*3)
  OFCvals=c(OFCvals,OFCacc)
}
vals
mean(vals)
sd(vals)

write.csv(vals,paste(sessiontoget,region,'CL','.csv'))
write.csv(OFCvals,paste(sessiontoget,region2,'CL','.csv'))
```

```{r}
#set.seed(8675309)
vals=c()
OFCvals=c()
samples=20
sessiontoget='STE1'
region='mPFC'
region2='OFC'

for (i in 1:40){
  train4=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region) %>% filter(Block=='4') %>% sample_n(samples)
  train3=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region) %>% filter(Block=='3') %>% sample_n(samples)
  train2=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region) %>% filter(Block=='2') %>% sample_n(samples)
  train1=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region) %>% filter(Block=='1') %>% sample_n(samples)
  train=rbind(train1,train2,train3,train4)
  
  OFCtrain4=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region2) %>% filter(Block=='4') %>% sample_n(samples)
  OFCtrain3=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region2) %>% filter(Block=='3') %>% sample_n(samples)
  OFCtrain2=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region2) %>% filter(Block=='2') %>% sample_n(samples)
  OFCtrain1=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region2) %>% filter(Block=='1') %>% sample_n(samples)
  OFCtrain=rbind(OFCtrain1,OFCtrain2,OFCtrain3,OFCtrain4)
  #train=transform(train, Block = sample(Block))
  #trainshuf=transform( train, Cluster = sample(Cluster))
  #lda.fitCV<-lda(Cluster~Pre*Post+tPre*tPost+Food,CV=TRUE,method='mle',data=train)
  lda.fitCV<-lda(Block~sk_Change+tk_Sum+tk_Food,CV=TRUE,data=train)
  OFClda.fitCV<-lda(Block~sk_Change+tk_Sum+tk_Food,CV=TRUE,data=OFCtrain)
  
  a=table(train$Block, lda.fitCV$class, dnn = c('Actual Group','Predicted Group'))
  acc=(a[16]+a[6]+a[11]+a[1])/(samples*4)
  vals=c(vals,acc)
  
  OFCa=table(OFCtrain$Block, OFClda.fitCV$class, dnn = c('Actual Group','Predicted Group'))
  OFCacc=(OFCa[16]+OFCa[6]+OFCa[11]+OFCa[1])/(samples*4)
  OFCvals=c(OFCvals,OFCacc)
}
vals
mean(vals)
sd(vals)

write.csv(vals,paste(sessiontoget,region,'BK','.csv'))
write.csv(OFCvals,paste(sessiontoget,region2,'BK','.csv'))

```



```{r}

vals=c()
OFCvals=c()
samples=20
sessiontoget='STPre'
region='mPFC'
region2='OFC'
weights=data.frame(metric=c('s','t','f'))


for (i in 1:40){

  train3=data2norm %>% filter(Cluster=='3') %>% filter(Region == region)%>% filter(sk_Session == sessiontoget)%>% sample_n(samples)
  train2=data2norm %>% filter(Cluster=='2') %>% filter(Region == region)%>% filter(sk_Session == sessiontoget)%>% sample_n(samples)
  train1=data2norm %>% filter(Cluster=='1') %>% filter(Region == region)%>% filter(sk_Session == sessiontoget)%>% sample_n(samples)
  train=rbind(train1,train2,train3)
  
  OFCtrain3=data2norm %>% filter(Cluster=='3') %>% filter(Region == region2)%>% filter(sk_Session == sessiontoget)%>% sample_n(samples)
  OFCtrain2=data2norm %>% filter(Cluster=='2') %>% filter(Region == region2)%>% filter(sk_Session == sessiontoget)%>% sample_n(samples)
  OFCtrain1=data2norm %>% filter(Cluster=='1') %>% filter(Region == region2)%>% filter(sk_Session == sessiontoget)%>% sample_n(samples)
  OFCtrain=rbind(OFCtrain1,OFCtrain2,OFCtrain3)
  #train=transform(train, Cluster = sample(Cluster))
  #trainshuf=transform( train, Cluster = sample(Cluster))
  #lda.fitCV<-lda(Cluster~Pre*Post+tPre*tPost,CV=TRUE,data=train)
  lda.fitCV<-lda(Cluster~sk_Change+tk_Sum+tk_Food,data=train)
  OFClda.fitCV<-lda(Cluster~sk_Change+tk_Sum+tk_Food,data=OFCtrain)
  
  saveweight=lda.fitCV$scaling[1:3]
  saveweightOFC=OFClda.fitCV$scaling[1:3]
  weights[i+1]<-c(saveweight)
  
  
  crosstest=predict(lda.fitCV,OFCtrain)
  crosstest2=predict(OFClda.fitCV,train)
  
  
  
  a=table(OFCtrain$Cluster, crosstest$class, dnn = c('Actual Group','Predicted Group'))
  acc=(a[1]+a[5]+a[9])/(samples*3)
  vals=c(vals,acc)
  
  
  OFCa=table(train$Cluster, crosstest2$class, dnn = c('Actual Group','Predicted Group'))
  OFCacc=(OFCa[1]+OFCa[5]+OFCa[9])/(samples*3)
  OFCvals=c(OFCvals,OFCacc)
}
vals
mean(vals)
sd(vals)

write.csv(vals,paste(sessiontoget,region,'CLcross','.csv'))
write.csv(OFCvals,paste(sessiontoget,region2,'CLcross','.csv'))
```


```{r}
#set.seed(8675309)
vals=c()
OFCvals=c()
samples=20
sessiontoget='STE1'
region='mPFC'
region2='OFC'

for (i in 1:40){
  train4=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region) %>% filter(Block=='4') %>% sample_n(samples)
  train3=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region) %>% filter(Block=='3') %>% sample_n(samples)
  train2=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region) %>% filter(Block=='2') %>% sample_n(samples)
  train1=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region) %>% filter(Block=='1') %>% sample_n(samples)
  train=rbind(train1,train2,train3,train4)
  
  OFCtrain4=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region2) %>% filter(Block=='4') %>% sample_n(samples)
  OFCtrain3=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region2) %>% filter(Block=='3') %>% sample_n(samples)
  OFCtrain2=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region2) %>% filter(Block=='2') %>% sample_n(samples)
  OFCtrain1=data2norm%>% filter(sk_Session == sessiontoget)%>% filter(Region == region2) %>% filter(Block=='1') %>% sample_n(samples)
  OFCtrain=rbind(OFCtrain1,OFCtrain2,OFCtrain3,OFCtrain4)
  train=transform(train, Block = sample(Block))
  #trainshuf=transform( train, Cluster = sample(Cluster))
  #lda.fitCV<-lda(Cluster~Pre*Post+tPre*tPost+Food,CV=TRUE,method='mle',data=train)
  lda.fitCV<-lda(Block~sk_Change+tk_Sum+tk_Food,data=train)
  OFClda.fitCV<-lda(Block~sk_Change+tk_Sum+tk_Food,data=OFCtrain)
  
  
  
  
  crosstest=predict(lda.fitCV,OFCtrain)
  crosstest2=predict(OFClda.fitCV,train)
  
  
  
  a=table(OFCtrain$Block, crosstest$class, dnn = c('Actual Group','Predicted Group'))
  acc=(a[16]+a[6]+a[11]+a[1])/(samples*4)
  vals=c(vals,acc)
  
  OFCa=table(train$Block, crosstest2$class, dnn = c('Actual Group','Predicted Group'))
  OFCacc=(OFCa[16]+OFCa[6]+OFCa[11]+OFCa[1])/(samples*4)
  OFCvals=c(OFCvals,OFCacc)
}
vals
mean(vals)
sd(vals)

write.csv(vals,paste(sessiontoget,region,'BKcrosss','.csv'))
write.csv(OFCvals,paste(sessiontoget,region2,'BKcross','.csv'))

```



#lda with 10 folds
```{r}
mae <- c()
chunks=443/10


data3 <- data2norm[sample(1:nrow(data2norm)), ]

for (i in 1:10){
  train_data <- data3[-((i*44-43):(i*44)), ]
  test_data <- data3[((i*44-43):(i*44)), ]
  m_lda <- lda(Cluster~Change+Food+Sum, data = train_data)
  m_pred <- predict(m_lda, test_data)
  mae <- c(mae, mean(abs( as.integer(m_pred$class == '1') - as.integer(test_data$Cluster == '1'))))
}


1-mean(mae)
1-mae
```
#QDA
```{r}
qda.fit<-qda(Cluster~Change+tSum+Food,data=train)
qda.fit
qda.pred<-predict(qda.fit,train)
mean(qda.pred$class==train$Cluster)
```

#naive bayes
```{r}
library(e1071)
nb.fit<-naiveBayes(Cluster~Change+tSum+Food,data=train)
nb.fit
nb.class<-predict(nb.fit,train)
mean(nb.class==train$Cluster)
tune(naiveBayes,Cluster~Change+tSum+Food,data=train)
```

#SVM
```{r}
samples=40
train3=data2norm %>% filter(Cluster=='3') %>% sample_n(samples)
train2=data2norm %>% filter(Cluster=='2') %>% sample_n(samples)
train1=data2norm %>% filter(Cluster=='1') %>% sample_n(samples)
train=rbind(train1,train2,train3)
#train=transform( train, Cluster = sample(Cluster))


#SVC
svm.fit<-svm(Cluster~Change.mp+take.mp,data=train,kernel='radial',cost=1,gamma=.1,scale=FALSE)
#fitted=svm.fit$decision.values
plot(svm.fit,train,Change.mp~take.mp)
summary(svm.fit)
#summary(svm.fit)




tune.out=tune(svm,Cluster~Change.mp+take.mp,data=train,kernel='radial',scale=FALSE,ranges=list(
  cost=c(.1,1,10,100,1000), gamma = c(.1,.5,1,2,4)))
summary(tune.out)
```


#ROC
```{r}
rocplot <- function(pred,truth,...){
  predob<-prediction(pred,truth)
  perf<-performance(predob, 'tpr','fpr')
  plot(perf,...)
}
par(mfrom=c(1,2))
rocplot(fitted,data2$Cluster,add=T)
```

